Generating Verified LLVM from Isabelle/HOL

### 2019-09-03 paper/main.tex
bugfixes

Integer instructions are defined on the \q{\is{n word}} type. For example, we define:
\begin{lstlisting}
  ll_udiv :: "n word => n word => n word"
  ll_udiv a b = do { assert (b ~= 0); return (a div b) }
\end{lstlisting}
where \q{\is{div}} is the unsigned division from Isabelle's word library.
Note the use of assertions to exclude undefined behavior, e.g., division by zero.

@@

llc_while :: ('a => 1 word llM) => ('a => 'a llM) => 'a => 'a llM
llc_while b c s = do {ctd <- b s; llc_if ctd (do {s <- c s; llc_while b c s}) (return s)}
\end{lstlisting}
That is, a block is a list of commands whose results are bound to variables, terminated by a return instruction. 
A command is either an instruction, a procedure call, or an if-then-else or while statement.
The arguments of instructions and procedure calls, as well as the condition of an if-then-else statement, must be variables or 
constants (i.e., numbers, the null pointer, or a zero-initialized value). 
The condition of a while statement is modeled as a block returning a \q{\is{1 word}}, such that it can be re-evaluated prior to each loop iteration.
%
A program is represented by a set of (monomorphic) theorems of the shape
\q{\is{proc\_i x_1 ... x\_n = cmd}},
where the \q{\is{proc\_i}} are Isabelle functions, the \q{\is{x\_i}} are variables, and all free variables on the right hand side are among the \q{\is{x\_i}}.
% As our monad allows arbitrary recursive definitions, we can define arbitrary recursive programs.

>>>>

Integer instructions are defined on the \q{\is{n word}} type. For example, we define:
\begin{lstlisting}
  ll_udiv :: "n word => n word => n word llM"
  ll_udiv a b = do { assert (b ~= 0); return (a div b) }
\end{lstlisting}
where \q{\is{div}} is the unsigned division from Isabelle's word library.
Note the use of assertions to exclude undefined behavior, e.g., division by zero.

@@

llc_while :: ('a => 1 word llM) => ('a => 'a llM) => 'a => 'a llM
llc_while b c s = do {ctd <- b s; llc_if ctd (do {s <- c s; llc_while b c s}) (return s)}
\end{lstlisting}
That is, a block is a list of commands whose results are bound to variables, terminated by a return instruction. 
A command is either an instruction, a procedure call, or an if-then-else or while statement.
The arguments of instructions and procedure calls, as well as the condition of an if-then-else statement, must be variables or 
constants (i.e., numbers, the null pointer, or a zero-initialized value). 
The condition of a while statement is modeled as a block returning a \q{\is{1 word}}, such that it can be re-evaluated prior to each loop iteration.
%
A program is represented by a set of (monomorphic) theorems of the shape
\q{\is{proc\_i x_1 ... x\_n = block}},
where the \q{\is{proc\_i}} are Isabelle functions, the \q{\is{x\_i}} are variables, and all free variables on the right hand side are among the \q{\is{x\_i}}.
% As our monad allows arbitrary recursive definitions, we can define arbitrary recursive programs.
